### 2018-02-05 written_docs/draft.Rmd
cross val with disparities

We also preregistered our explicit bias as a simple feeling thermometer towards balcks (i.e. *how warm or cold do you feel towards Blacks? 0=very cold, 10=very warm*). However, past research [@leitner2016blacks; @hehman2017disproportionate] has used the difference in reported warmth towards whites and blacks, and so we in the main text, we report models using this metric of explicit bias. Additionally, we preregistered analyses with poststratified estimates (as presented in the main text) along with raw, county-based means. Finally, we had not known about the issues with juvenile justice facilities, or with the school districts with reporting errors. Here, we present the results of the preregistered analyses exactly.

#Simple county means

>>>>

We also preregistered our explicit bias as a simple feeling thermometer towards balcks (i.e. *how warm or cold do you feel towards Blacks? 0=very cold, 10=very warm*). However, past research [@leitner2016blacks; @hehman2017disproportionate] has used the difference in reported warmth towards whites and blacks, and so in the main text, we report models using this metric of explicit bias. Additionally, we preregistered analyses with poststratified estimates (as presented in the main text) along with raw, county-based means. Finally, we had not known about the issues with juvenile justice facilities, or with the school districts with reporting errors. Here, we present the results of the preregistered analyses exactly.

#Simple county means
```{r cross_val_county_means}
"%ni%" <- Negate("%in%")
df <- read.csv('/Users/travis/Documents/gits/educational_disparities/cluster/data/county_grouping.csv')
f <- list.files('/Users/travis/Documents/gits/educational_disparities/cluster/output/metrics_raw/corporal/')

test_summary_dat <- data.frame(file=f, 
                               r_2 = NA,
                               r_2_lower=NA,
                               r_2_upper=NA)
j=1
for (i in f){
  print(i)
  load(paste('/Users/travis/Documents/gits/educational_disparities/cluster/output/metrics_raw/inschool_susp/', i, sep=''))
  model <- m
  testing_model <- sample(f[f %ni% i], 1)
  load(paste('/Users/travis/Documents/gits/educational_disparities/cluster/output/metrics_raw/inschool_susp/', testing_model, sep=''))
  m$data$bias <- m$data$bias[,1]
  m$data$warmth <- m$data$warmth[,1]
  m$data$weighted_bias <- m$data$weighted_bias[,1]
  m$data$weighted_warmth <- m$data$weighted_warmth[,1]
  m$data$total_pop <- m$data$total_pop[,1]
  m$data$unemp_rate <- m$data$unemp_rate[,1]
  m$data$med_income <- m$data$med_income[,1]
  m$data$poverty_rate <- m$data$poverty_rate[,1]
  m$data$col_grads <- m$data$col_grads[,1]
  m$data$white_prop <- m$data$white_prop[,1]
  m$data$black_prop <- m$data$black_prop[,1]
  m$data$b.w.ratio <- m$data$b.w.ratio[,1]
  m$data %>%
    filter(!is.na(bias)) %>%
    filter(!is.na(warmth)) %>%
    filter(!is.na(weighted_bias)) %>%
    filter(!is.na(weighted_warmth)) %>%
    filter(!is.na(total_pop)) -> testing_data
  y_hat <- data.frame(t(posterior_predict(m, draws = 250, newdata = testing_data)))
  y_hat$index <- seq(1, length(y_hat$X1))
  testing_data <- cbind(testing_data, y_hat)
  testing_data %>%
    gather(sample, pred, X1:X250) %>%
    group_by(sample) %>%
    summarise(r = cor(number, pred)^2) %>%
    summarise(r_2 = mean(r),
              r_2_lower = quantile(r, .25),
              r_2_upper = quantile(r, .75)) -> r2
  test_summary_dat[j,2:4] <- r2
  j = j+1
}

test_summary_datweighted <- data.frame(file=f, 
                               r_2 = NA,
                               r_2_lower=NA,
                               r_2_upper=NA)
j=1
for (i in f){
  print(i)
  load(paste('/Users/travis/Documents/gits/educational_disparities/cluster/output/metrics_weighted/older_run/inschool_susp/', i, sep=''))
  model <- m
  testing_model <- sample(f[f %ni% i], 1)
  load(paste('/Users/travis/Documents/gits/educational_disparities/cluster/output/metrics_weighted/older_run/inschool_susp/', testing_model, sep=''))
  m$data$bias <- m$data$bias[,1]
  m$data$warmth <- m$data$warmth[,1]
  m$data$weighted_bias <- m$data$weighted_bias[,1]
  m$data$weighted_warmth <- m$data$weighted_warmth[,1]
  m$data$total_pop <- m$data$total_pop[,1]
  m$data$unemp_rate <- m$data$unemp_rate[,1]
  m$data$med_income <- m$data$med_income[,1]
  m$data$poverty_rate <- m$data$poverty_rate[,1]
  m$data$col_grads <- m$data$col_grads[,1]
  m$data$white_prop <- m$data$white_prop[,1]
  m$data$black_prop <- m$data$black_prop[,1]
  m$data$b.w.ratio <- m$data$b.w.ratio[,1]
  m$data %>%
    filter(!is.na(bias)) %>%
    filter(!is.na(warmth)) %>%
    filter(!is.na(weighted_bias)) %>%
    filter(!is.na(weighted_warmth)) %>%
    filter(!is.na(total_pop)) -> testing_data
  y_hat <- data.frame(t(posterior_predict(m, draws = 250, newdata = testing_data)))
  y_hat$index <- seq(1, length(y_hat$X1))
  testing_data <- cbind(testing_data, y_hat)
  testing_data %>%
    gather(sample, pred, X1:X250) %>%
    group_by(sample) %>%
    summarise(r = cor(number, pred)^2) %>%
    summarise(r_2 = mean(r),
              r_2_lower = quantile(r, .25),
              r_2_upper = quantile(r, .75)) -> r2
  test_summary_datweighted[j,2:4] <- r2
  j = j+1
}
